### 2024-01-04 tesis_Ashish/Chapter4/chapter4.tex
Updated thesis 4 Jan 2024

\begin{table}[htbp]
  \centering
  \caption[2018 Luminosity systematic uncertainty]{Systematic uncertainty during calibration and physics data taking for the final veto.}
\label{tab:systematic-uncertainty}
\begin{tabular}{cccc}
  \textbf{}&\textbf{Systematics} &\textbf{Uncertainty [\%]} \\
\hline
Normalization  Length scale & -  \\
 & Orbit drift &  -  \\
 & x-y nonfactorization & - \\
 & Beam-beam deflection + Dynamic $\beta^{*}$  & - \\
 & Beam current calibration  & - \\
 & Ghost and satellite & - \\
 & Scan to scan variation & 0.3 \\
 & Bunch to bunch variation & 0.1 \\
 & Cross detector consistency  & 0.5 \\
 & Background subtraction  & 0.1 \\
Integration & Afterglow  &  0.3 \\
 & Cross detector stability & 0.3 \\
 & Linearity  & 0.4 \\
%Total &  &  1.08 \\
\end{tabular}
%\caption[Systematic uncertainty]{Systematic uncertainty during calibration and physics data taking for PAS and final veto.}
\label{tab:systematic-uncertainty}
\end{table}

>>>>

\begin{table}[htbp]
  \centering
  \caption[2018 Luminosity systematic uncertainty]{Systematic uncertainty during calibration and physics data taking for the final veto.}
\label{tab:systematic-uncertainty}
\begin{tabular}{cccc}
  \textbf{}&\textbf{Systematics} &\textbf{Uncertainty [\%]} \\
\hline
Normalization  & Length scale & -  \\
 & Orbit drift &  -  \\
 & x-y nonfactorization & - \\
 & Beam-beam deflection + Dynamic $\beta^{*}$  & - \\
 & Beam current calibration  & - \\
 & Ghost and satellite & - \\
 & Scan to scan variation & 0.3 \\
 & Bunch to bunch variation & 0.1 \\
 & Cross detector consistency  & 0.5 \\
 & Background subtraction  & 0.1 \\
Integration & Afterglow  &  0.3 \\
 & Cross detector stability & 0.3 \\
 & Linearity  & 0.4 \\
%Total &  &  1.08 \\
\end{tabular}
%\caption[Systematic uncertainty]{Systematic uncertainty during calibration and physics data taking for PAS and final veto.}
\label{tab:systematic-uncertainty}
\end{table}
